Bare minimum: order theory

### 2025-09-11 BareMinima/OrderTheory/BareMinimumOrderTheory.tex
OrderTheory: more work on the bare minimum

@@

\begin{defn}[Upper and lower bounds]
	Let $P$ be an \marginleft{Upper/Lower bounds} ordered set and let $A \subseteq P$. An \textbf{upper bound} (or \textbf{lower bound}) is an element $p \in P$ such that $a \leq p$ (or $p \leq a$) for all $a \in A$.
\end{defn}

\begin{remark}
	The upper/lowers bound of $A$ are not necessarily in $A$.
\end{remark}

@@

\begin{defn}[Lattice properties]
	We define\marginleft{Complete, distributive, complemented} the following additional properties on lattices:
	\begin{description}
		\item[Completeness.] A lattice is \textbf{complete} if all subsets have joins and meet, not just finite ones.
		\item[Distributivity.] A lattice is \textbf{distributive} if it satisfies
		\begin{align*}
			a \vee (b \wedge c) = (a \vee b) \wedge (a \vee c) \\
			a \wedge (b \vee c) = (a \wedge b) \vee (a \wedge c).
		\end{align*}
		A complete lattice is \textbf{infinitely distributive} if the same holds over infinite operations.
		\item[Complemented.] A bounded lattice is \textbf{complemented} if every element has a complement. It is uniquely complement if the complement is unique.
		\item[Ortho-complemented.] A bounded lattice is \textbf{complemented} if every element has a unique complement.
	\end{description}
\end{defn}

@@

\begin{defn}[Maximal subsets]
	A linearly \marginleft{Maximal subset} ordered subset is \textbf{maximal} if it is not a scrict subset of another linearly ordered subset.
\end{defn}

\begin{prop}[Kuratowski's Lemma]
	Every linearly ordered subset is the subset of some maximal linearly ordered subset.
\end{prop}

>>>>

\begin{defn}[Maximal subsets]
	A linearly \marginleft{Maximal subset} ordered subset (i.e. a chain) is \textbf{maximal} if it is not a scrict subset of another linearly ordered subset.
\end{defn}

\begin{prop}[Kuratowski's Lemma or Hausdorff maximal principle]
	Every linearly ordered subset is the subset of some maximal linearly ordered subset.
\end{prop}

\begin{prop}
	Kuratowski's Lemma is equivalent to the axiom of choice.
\end{prop}

@@

\begin{defn}[Upper and lower bounds]
	Let $X$ be an \marginleft{Upper/Lower bounds} ordered set and let $A \subseteq X$. An \textbf{upper bound} (or \textbf{lower bound}) is an element $x \in X$ such that $a \leq x$ (or $x \leq a$) for all $a \in A$.
\end{defn}

@@

\begin{defn}[Lattice properties]
	We define\marginleft{Complete, distributive, complemented} the following additional properties on lattices:
	\begin{description}
		\item[Completeness.] A lattice is \textbf{complete} if all subsets have joins and meet, not just finite ones.
		\item[Modularity.] A lattice is \textbf{modular} if $a \leq b$ implies $a \vee (c \wedge b) = (a \vee c) \wedge b$
		\item[Distributivity.] A lattice is \textbf{distributive} if it satisfies
		\begin{align*}
			a \vee (b \wedge c) = (a \vee b) \wedge (a \vee c) \\
			a \wedge (b \vee c) = (a \wedge b) \vee (a \wedge c).
		\end{align*}
		A complete lattice is \textbf{infinitely distributive} if the same holds over infinite operations.
		\item[Complemented.] A bounded lattice is \textbf{complemented} if every element has a complement. It is uniquely complement if the complement is unique.
		\item[Orthocomplemented.] A bounded lattice is \textbf{orthocomplemented} if for every element $a$ there is a complement $a^{\bot}$ such that $a^{\bot\bot} = a$ and if $a \leq b$ then $b^{\bot} \leq a^{\bot}$
		\item[Orthomodular.] A lattice is \textbf{orthomodular} if it is orthocomplemented and if $a \leq b$ implies $a \vee (a^{\bot} \wedge b) = (a \vee a^{\bot}) \wedge b$ (i.e. modularity holds at least of orthocomplements)
	\end{description}
\end{defn}

\begin{prop}
	Every distributive lattice is a modular. Every complete lattice is bounded.
\end{prop}

@@
